MSOA Industrial Electricty and Gas maps

### 2021-08-19 LSOA domestic Elec and Gas.Rmd
Fixing Typo errors

```{r Mapping the LSOA difference in mean dom elec consumption}
# merge to sf geometry on LSOA11CD
lsoa_sf_de20102019<-merge(lsoa_sf_data, merged_de)
ggplot2::ggplot(lsoa_sf_de20102019, aes(fill=de_diff))+
                  geom_sf() +
                  scale_fill_continuous(name="Change in Mean comsumpton (kWh per meter)",low="green",high="red") +
  labs(caption="Solent(all LSOAs)")
```

#####Cities in more detail
```{r Southampton LSOA difference in dom Elec}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LAD11NM == "Southampton")
# plotting the electricity consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de_diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth LSOA difference in dom Elec}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LAD11NM == "Portsmouth")
# plotting the electricity consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de-diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA difference in dom Elec}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LAD11NM == "Winchester")
# plotting the electricity consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de_diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Winchester")
```

>>>>

```{r Mapping the LSOA difference in mean dom elec consumption}
# merge to sf geometry on LSOA11CD
lsoa_sf_de20102019<-merge(lsoa_sf_data, merged_de)
ggplot2::ggplot(lsoa_sf_de20102019, aes(fill=de_diff))+
                  geom_sf() +
                  scale_fill_continuous(name="Change in Mean comsumpton (kWh per meter)",low="green",high="red") +
  labs(caption="Solent(all LSOAs)")

lsoa_sf_de20102019$pc_diff <- 100*(lsoa_sf_de20102019$de_diff/lsoa_sf_de20102019$de2010)
t_diff <-  dplyr::select(as.data.frame(lsoa_sf_de20102019), 
                         LSOA11CD, `Lower Layer Super Output Area (LSOA) Name.y`,
                         de2010, de2019, de_diff, pc_diff)
head(arrange(t_diff, pc_diff))
head(arrange(t_diff, -pc_diff))
ggplot2::ggplot(t_diff, aes(x = pc_diff)) +
  geom_histogram()
```

#####Cities in more detail
```{r Southampton LSOA difference in dom Elec}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LSOA11CD == "Southampton")
# plotting the electricity consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de_diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Southampton")
#BROKEN
```
```{r Portsmouth LSOA difference in dom Elec}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LAD11NM == "Portsmouth")
# plotting the electricity consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de-diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA difference in dom Elec}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LAD11NM == "Winchester")
# plotting the electricity consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de_diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Winchester")
```

### 2021-08-19 MSOA non domestic Elec and Gas.Rmd
Fixing Typo errors

####Mapping the difference in non domestic gas from 2010 to 2019 
```{r Creating the difference in non domestic gas consumption in the MSOA}
msoa_2010_ndgas<-readr::read_csv(paste0(dataFolder,"/energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2010.csv"))
msoa_2019_ndgas<-readr::read_csv(paste0(dataFolder,"energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2019.csv"))
msoa_2010_ndgas$ndgas2010<-msoa_2010_ndgas$'Mean consumption (kWh per meter)'
msoa_2019_ndgas$ndgas2019<-msoa_2019_ndgas$'Mean consumption (kWh per meter)'
merged_ndgas20102019<-merge(msoa_2010_ndgas, msoa_2019_ndgas, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_ndgas20102019)
merged_ndgas20102019$ndgas_diff<-merged_ndgas20102019$nondomgas2019 - merged_nd20102019$nondomgas2010 ##BROKEN
summary(merged_nondomgas20102019)
```

```{r Mapping the change in non domestic gas usage in the MSOA}
merged_nondomgas20102019$MSOA11CD <- merged_df$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
msoa_nondomgas20102019 <- merge(msoa_sf_data, merged_nondomgas20102019) #merging these
ggplot2::ggplot(msoa_nondomgas20102019) +
  geom_sf(aes(fill=ndgas_diff))+ 
  scale_fill_continuous(name="Change in mean gas consumption in the indistrial sector", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
##BROKEN
```

>>>>

####Mapping the difference in non domestic gas from 2010 to 2019 
```{r Creating the difference in non domestic gas consumption in the MSOA}
msoa_2010_ndgas<-readr::read_csv(paste0(dataFolder,"/energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2010.csv"))
msoa_2019_ndgas<-readr::read_csv(paste0(dataFolder,"energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2019.csv"))
msoa_2010_ndgas$ndgas2010<-msoa_2010_ndgas$'Mean consumption (kWh per meter)'
msoa_2019_ndgas$ndgas2019<-msoa_2019_ndgas$'Mean consumption (kWh per meter)'
merged_ndgas20102019<-merge(msoa_2010_ndgas, msoa_2019_ndgas, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_ndgas20102019)
merged_ndgas20102019$ndgas_diff<-merged_ndgas20102019$ndgas2019 - merged_ndgas20102019$ndgas2010 ##BROKEN
summary(merged_ndgas20102019)
```

```{r Mapping the change in non domestic gas usage in the MSOA}
merged_ndgas20102019$MSOA11CD <- merged_df$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
msoa_ndgas20102019 <- merge(msoa_sf_data, merged_ndgas20102019) #merging these
ggplot2::ggplot(msoa_ndgas20102019) +
  geom_sf(aes(fill=ndgas_diff))+ 
  scale_fill_continuous(name="Change in mean gas consumption in the indistrial sector", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
##BROKEN
```
